---
title: "learning by doing"
author: "Moses Kayanda"
date: "2/18/2020"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Write a function that adds two numbers, and divides the result by 2

```{r}
add <- function(x, y) {
  return((x + y)/2)
}
```
## 2. You can take a subset of a string using the substr function. First, using that
function to extract the first characters of a bit of text. Then, write a function called
firstTwoChars that extracts the first two characters of any bit of text.
```{r}
firstTwoChars <- function(text){
  substr(text,1,2)
}

firstTwoChars("HS611")
  
```
## 3. Write a function that checks if there are any missing values in a vector (using
is.na and any). The function should return TRUE if there are missing values, and
FALSE if not.
```{r}
# conditional statement returns TRUE if x is not NA, FALSE otherwise
missing_value <- function(x){
  if(any(is.na(x))){
    T
} else{
  F
}
}
x <- c(2,3,4,5,NA,6.7)
y <- c(2,3,4,5,9,6.7)
missing_value(x)
missing_value(y)
```
## 4. Improve the function so that it tells you which of the values are missing, if any
(Hint: use the which function).
```{r}
missing_value <- function(x){
  if(any(is.na(x))){
    return(which(is.na(x)))
  } else{
    return("No missing value")
  }
}
x <- c(2,3,4,5,NA,6.7)
y <- c(2,3,4,5,9,6.7)
missing_value(x)
missing_value(y)
```
## 5. The function readline can be used to ask for data to be typed in. First, figure out
how to use readline by reading the corresponding help file. Then, construct a
function called getAge that asks the user to type his/her age. (Hint: check the
examples in the readline help page). The getAge function will return the age of
the user like "Really you are 28 years old ?" if the user enters 28 as input. If user
enters a non-numeric character or blank string the function will return: “This is not
a valid age, please re-enter ”
```{r}
getAge <- function() {
  ANSWER <- readline("Please type your age? ")
  ANSWER<- suppressWarnings(as.numeric(answer))
  if(is.na(ANSWER)){
    cat("This is not a valid age, please re-enter")
    getAge()
  }else{
    cat("Really you are, ANSWER, years old")
}
}
getAge(21)
```
## 6. Write a function that returns the confidence interval for a vector. The function
should have two inputs: the vector, and the desired ’alpha’.

```{r}
confidence_interval <- function(v,alpha){
  xbar<-mean(v)
  s<-sd(v)
  n<-length(v)
  half.width<-qt(1-alpha/2, n-1)*s/sqrt(n)
  c(xbar - half.width, xbar + half.width)
}
confidence_interval(c(2,4,7),.01)
```

